

Since the data is very small, I just show a demo plot here, which to demonstrate the user's activity
and sleep quality by month among the calender year.
```{r}
### format the data by monthly segmentations
df<-read.csv('OneYearFitBitDataSleep.csv')
month<-apply(df,1,function(x) paste(substr(toString(x),7,10),'-',substr(toString(x),4,5),sep=''))
monthly_sleep<-cbind(month,df)

df<-read.csv('OneYearFitBitData.csv')
month<-apply(df,1,function(x) paste(substr(toString(x),7,10),'-',substr(toString(x),4,5),sep=''))
monthly_activity<-cbind(month,df)

```
From the plots we can have a general insight about the user's calories burned in the past year.
In winter, the user tends to have less walking or sporting than during summer. 
```{r}
f<-aggregate(Calorie.bruciate~month,monthly_activity,mean)
plot(f)
```
Similarly, we can check the user's sleeping quality during the past year. Given limited columns,
we could define the quality of sleep as the ratio of actual sleeping time and rest time (sleeping+awake),
with non-sense date filtered out. From the plot we can see the user's sleep quality improves during the last year,
however recently drops a little bit in summer 2016, with more information given, we would like to explore
the potential factors involved in sleep regulation.
```{r}
m<-monthly_sleep
f<-cbind(m[,c(1,2)],m[,3]/m[,6])
colnames(f)[3]<-"quality"
f<-f[(!is.na(f[,3])),]
f<-aggregate(quality~month,f,mean)
plot(f)
```
